---
title: "Assignment 1"
---

# Assignment 1

My first assignment has two parts.

## (a)Brief Summary of Cem Vardar

Cem Vardar is an industrial engineer who graduated from Arizona State University with a bachelor's degree and a doctorate.He began his career as an intern at Intel before learning about the connection between data science and analytics at Carvana.Data science and industrial engineering are primarily concerned with the management and optimization of complex systems. To solve organizational issues and improve the effectiveness of logistics systems, industrial engineers employ modeling and simulation.By turning data into information, data science enables decision-makers to monitor measures like profitability and sales. Additionally, subjects like funnel analysis and quick delivery are crucial. To provide value to firms, data scientists must possess analytical thinking and data reading abilities. Additionally covered are the value of a master's degree and the effect internships have on business.It highlights the significance of personal growth and pursuing interests, as well as the effects of artificial intelligence and entrepreneurship on industrial engineering.

Question 1 : What is funnel analysis and how is it important for businesses?

Answer: Funnel analysis is a process that follows a business's potential customers all the way to the purchase stage. This analysis is used to understand and optimize the different stages of the customer journey.

Question 2 : What is the purpose of net lift modeling?

A\) To reduce lead times to increase customer satisfaction.

B\) Measure the impact of marketing campaigns and increase reach to the target audience.

C\) To manage and optimize product inventory levels.

D\) Organizing training programs to increase employee productivity.

Correct Answer: B) Measuring the impact of marketing campaigns and increasing the reach of the target audience.

## (b)Polls_us_election_2016

```{r}
#Import data
library(dslabs)
data("polls_us_election_2016")
head(polls_us_election_2016, 10)
```

```{r}
#Total NA
total_na<- sum(is.na(polls_us_election_2016))
total_na
```

```{r}
#Replacing NA
complete_pool_data<-polls_us_election_2016
birth_year<-2000
first_name<-"Necati"
for (col in names(complete_pool_data)){
  if(is.numeric(complete_pool_data[[col]])){
    complete_pool_data[[col]]<-ifelse(is.na(complete_pool_data[[col]]),birth_year,complete_pool_data[[col]])
  }
  else if(is.character(complete_pool_data[[col]])|| is.factor(complete_pool_data[[col]])){
    complete_pool_data[[col]]<-ifelse(is.na(complete_pool_data[[col]]),first_name,as.character(complete_pool_data[[col]]))
   }
  }
 

```

```{r}
#Display the first 10 row and number of NA's  
complete_pool_data_ten_row<-head(complete_pool_data,10) 
complete_pool_data_ten_row

total_na<-sum(is.na(complete_pool_data))
total_na


```
